\section{Introduction}
\label{sec:intro}

Drug repurposing---identifying new therapeutic uses for existing drugs---offers a cost-effective path toward addressing unmet medical needs, with computational approaches increasingly relying on biomedical knowledge graphs (KGs) to model the complex web of drug-disease-gene interactions~\citep{chandak2023building, huang2024zero}.
These KGs are inherently dynamic: databases such as DrugBank, DisGeNET, and the Gene Ontology are updated on monthly or quarterly cycles, introducing new entities, relations, and revised annotations.
Retraining KG embedding models from scratch after each update is computationally prohibitive and discards previously learned representations.
Continual learning offers a principled alternative, enabling models to incrementally assimilate new knowledge while preserving past competencies.
However, naive sequential fine-tuning on new graph snapshots leads to \emph{catastrophic forgetting}~\citep{kirkpatrick2017overcoming}, where performance on previously learned facts degrades substantially.

Existing continual knowledge graph embedding (CKGE) methods---including EWC-based regularization~\citep{kirkpatrick2017overcoming}, experience replay~\citep{rolnick2019experience}, and the LKGE framework~\citep{cui2023lifelong}---address forgetting exclusively through the lens of graph structure.
They treat KG entities as featureless identifiers and apply uniform regularization across all model parameters, implicitly assuming that all components forget at the same rate.
This assumption is fundamentally flawed in modern biomedical KGs where entities carry rich multimodal attributes: textual descriptions from medical ontologies, molecular fingerprints from chemical databases, and functional annotations from gene ontologies.
These modalities provide complementary signals---a drug's molecular structure constrains its binding targets, while its textual description captures clinical context---yet no existing CKGE method leverages or protects them.

We propose \fullname (\ours), the first continual learning framework that is both natively multimodal and modality-aware.
\ours introduces three key innovations:
\textbf{(1) Modality-Aware Elastic Weight Consolidation (MA-EWC)}, which maintains separate Fisher information matrices for structural, textual, and molecular encoder parameters and applies independently tuned regularization strengths, reflecting the empirical observation that structural parameters are more forgetting-prone than molecular ones;
\textbf{(2) Multimodal Memory Replay}, which selects diverse exemplars via K-means clustering on structural embeddings to populate a fixed-size replay buffer, ensuring that replayed triples cover topologically distinct regions of the graph; and
\textbf{(3) Cross-Modal Attention Fusion}, which uses bidirectional cross-attention with four heads to enable each modality to attend to complementary information from the others before producing a unified entity representation.

On the PrimeKG-CL benchmark---a continual learning testbed with 129K+ entities, 8.1M+ edges, and 10 temporal link prediction tasks derived from real-world database updates---\ours achieves an average performance (AP) of $0.063$, outperforming the strongest continual baseline LKGE ($0.039$) by $1.6\times$ and Joint Training ($0.018$) by $3.5\times$.
On continual node classification, \ours attains AP\,=\,$0.431$, exceeding Joint Training by $16\%$.
These gains confirm that multimodal representations provide substantial advantages for KG reasoning, particularly when combined with modality-aware continual learning mechanisms.

\input{tables/comparison}

Our contributions are as follows:
\begin{enumerate}
    \item We identify and characterize the phenomenon of \emph{modality-specific forgetting} in continual biomedical KG learning, showing that structural, textual, and molecular encoders exhibit distinct forgetting dynamics.
    \item We propose \ours, the first continual KG learning method that jointly encodes structural, textual, and molecular modalities and protects them with modality-aware regularization and diverse replay.
    \item We introduce modality-aware EWC with per-modality Fisher matrices and independently tuned regularization strengths, enabling fine-grained forgetting control.
    \item We demonstrate state-of-the-art continual link prediction and node classification performance on PrimeKG-CL, with thorough analysis of the interplay between multimodal representations and continual learning.
\end{enumerate}
